---
title: "Homework 2"
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.

```{r}
#Setup
library(dplyr)
library(ggplot2)
library(forcats)
library(scales)

country_lists <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-09-09/country_lists.csv')
rank_by_year <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-09-09/rank_by_year.csv')

# Find difference in improvement 
start <- rank_by_year %>%
  group_by(country) %>%
  arrange(year) %>%
  slice(1) %>%
  ungroup() %>%
  transmute(country,
            start_year  = year,
            start_count = visa_free_count,
            start_rank  = rank)

end <- rank_by_year %>%
  group_by(country) %>%
  arrange(desc(year)) %>%
  slice(1) %>%
  ungroup() %>%
  transmute(country,
            end_year  = year,
            end_count = visa_free_count,
            end_rank  = rank)

improve <- start %>%
  inner_join(end, by = "country") %>%
  mutate(
    delta_count = end_count - start_count,      # ↑ visa-free destinations
    delta_rank  = start_rank - end_rank         # ↑ positive = better (rank number fell)
  ) %>%
  arrange(desc(delta_count))

# Choose top 10 movers
top <- improve %>% slice_max(delta_count, n = 10, with_ties = FALSE)

yr_min <- min(rank_by_year$year, na.rm = TRUE)
yr_max <- max(rank_by_year$year, na.rm = TRUE)
```
```{r}
#Viz
ggplot(top, aes(y = fct_reorder(country, delta_count))) +
  geom_segment(aes(x = start_count, xend = end_count, yend = country), color = "grey70", linewidth = 1.6, lineend = "round") +
  geom_point(aes(x = start_count), size = 3, color = "#9aa0a6") +
  geom_point(aes(x = end_count),   size = 3.2, color = "#2C7FB8") +
  geom_text(aes(x = end_count, label = paste0("+", delta_count)), hjust = -0.15, size = 3) +
  scale_x_continuous(labels = number,
                     limits = c(0, max(top$end_count) * 1.15)) +
  labs(
    title = "Improvements in passport power",
    subtitle = paste0("Increase in visa-free/visa-on-arrival destinations, ", yr_min, "–", yr_max),
    x = "Visa-free count (endpoints show first vs last year)",
    y = NULL) +
  theme_minimal(base_size = 11) +
  theme(panel.grid.major.y = element_blank())
```
# EXPLANATION

My chart answers the question, "Which countries have made the most dramatic improvements in passport power?" by ranking countries by the increase in visa-free (or visa-on-arrival) destinations from the first to the last year in the dataset. Each row is a country and the dumbbell shows its startin count and ending count with the segment length and the +label indicating the magnitude of improvement. As shown, the Vatican City and UAE had considerable improvements in "passport power" from 2006-2025. 

