---
title: "Homework 04"
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.

Which clubs in EuroLeage have been the most successful historically?
```{r}
# Read data
euro <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-10-07/euroleague_basketball.csv')
```
```{r}
library(tidyverse)
library(dplyr)
top <- euro %>%
  mutate(
    Titles_Won = coalesce(Titles_Won, 0),
    FinalFour_Appearances = coalesce(FinalFour_Appearances, 0)
  ) %>%
  arrange(desc(Titles_Won), desc(FinalFour_Appearances)) %>%
  slice_head(n = 15) %>%                     # top clubs
  mutate(Team = forcats::fct_inorder(Team))

ggplot(top, aes(Team, Titles_Won)) +
  geom_col() +
  geom_text(aes(label = paste0(Titles_Won, " titles | ", FinalFour_Appearances, " FF")),
            hjust = -0.1, size = 3) +
  coord_flip() +
  expand_limits(y = max(top$Titles_Won) + 1) +
  labs(x = NULL, y = "EuroLeague titles",
       title = "Most Historically Successful EuroLeague Clubs")
```
As shown in the Viz, Panathinaikos of Greece is the most succesful club in EuroLeague historically 

