---
title: "Homework 05"
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.

If you wanted to see thousands of cranes, when is the best time of year to visit?

```{r}
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)

cranes <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-09-30/cranes.csv')
```
```{r}
#Change threshold to 1000 cranes
thr <- 1000  

cranes_clean <- cranes %>%
  filter(is.na(weather_disruption) | weather_disruption==FALSE)

by_month <- cranes_clean %>%
  mutate(month=factor(month(date,label=TRUE,abbr=TRUE),levels=month.abb)) %>%
  group_by(month) %>%
  summarise(days_1k=sum(observations>=thr,na.rm=TRUE),
            peak=max(observations,na.rm=TRUE),
            total=sum(observations,na.rm=TRUE), .groups="drop") %>%
  arrange(desc(days_1k),desc(peak),desc(total))

best <- by_month %>% slice_max(days_1k, n=1, with_ties=TRUE)

cat(
  "Best time to see thousands of cranes:\n",
  paste0(best$month, collapse=", "),
  "  — Months that have the most days with ≥ ",thr," cranes (peak in top month = ",
  max(best$peak,na.rm=TRUE), ").\n", sep=""
)

# Viz
ggplot(by_month, aes(month, days_1k)) +
  geom_col() +
  geom_hline(yintercept=max(by_month$days_1k,na.rm=TRUE), linetype=2) +
  labs(x=NULL, y=paste0("Days with ≥ ",thr," cranes"),
       title="When do thousands of cranes show up?",
       subtitle="Excl. weather disruptions") +
  theme_minimal(base_size = 12)
```




